---
title: "DAS-Project2"
author: "Yiheng Yang"
format: pdf
editor: visual
execute:
  warning: false
---

# load the data

```{r}
data=read.csv("dataset04.csv")
```

# get packages

```{r}
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(tidyverse)
library(ggplot2)
library(MASS)
library(knitr)
library(tidyr)
library(gt)
library(janitor)
```

# explanatory analysis

```{r}
data%>%summarize('Mean' = mean(Total.Number.of.Family.members),
'Median' = median(Total.Number.of.Family.members),
'St.Dev' = sd(Total.Number.of.Family.members),
'Variance'=var(Total.Number.of.Family.members),
'Min' = min(Total.Number.of.Family.members),
'Max' = max(Total.Number.of.Family.members),
'IQR' = quantile(Total.Number.of.Family.members,0.75)-quantile(Total.Number.of.Family.members,0.25),
'Sample_size' = n())%>% 
  gt()%>%
  fmt_number(decimals=2)%>%
  cols_label(
Mean = html("Mean"),
Median = html("Median"),
St.Dev = html("Std. Dev"),
Variance=html("Variance"),
Min = html("Minimum"),
Max = html("Maximum"),
IQR = html("Interquartile Range"),
Sample_size = html("Sample Size"))
```

We can see from this numerical summary, the mean of number of family members is 4.53 and the variance is 4.91. If variance is bigger than mean, we can determine that we have overdispersion. We will investigate this phenomenon later.

# convert some categorical variables to factors

```{r}
data$Household.Head.Sex=as.factor(data$Household.Head.Sex)
data$Type.of.Household=as.factor(data$Type.of.Household)
data$Electricity=as.factor(data$Electricity)
levels(data$Electricity)=c("No","Yes")
data$Number.of.bedrooms=as.factor(data$Number.of.bedrooms)
levels(data$Number.of.bedrooms)=c("0","1","2","3","4","5","6","7")
```

# Graphical summaries

As we want to plot a boxplot with x axis to be number of family members, so we need to change this variable to be a factor.

```{r}
data$Total.Number.of.Family.members=as.factor(data$Total.Number.of.Family.members)
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Total.Household.Income,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Total Household Income",title="Income of families with different number of family members ")
```

We can see from the above boxplot that the median of household income increase as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Total.Food.Expenditure,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Total food expenditure",title="Food expenditure of families with different number of family members ")
```

The boxplot indicates that median increase significantly as the number of family members increase. Household with 19 members have the largest variance in food expenditure.

```{r}
data%>%
  tabyl(Household.Head.Sex,Total.Number.of.Family.members)%>%
  adorn_percentages()%>%
  adorn_pct_formatting()%>%
  adorn_ns()
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Household.Head.Sex))+geom_bar(aes(y=..prop..,fill=Household.Head.Sex),position="dodge")+labs(x="Number of Family Members",y="Proportion",title="Head sex proportion for different size of households")
```

We can see from the barplot, for those small sized households, the proportion is much higher for females than for males. However, this situation does not exist for those household with four or more family members.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Household.Head.Age,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Household head age",title="Head age for different size households")
```

For different size of households, the median of household head age remain at a constant level around 50.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Type.of.Household))+geom_bar(aes(y=..prop..,fill=Type.of.Household))+labs(x="Number of Family Members",y="Proportion",title="Type of household in different size of households")
```

These families with two or more nonrelated members only exist in medium size household. As total family members increase more than 8, single family account for a very small proportion.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=House.Floor.Area,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="House floor area",title="House floor area for different size of households")
```

For different sizes of households, there are a few outliers. And the median of house floor area seems to be stable as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=House.Age,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="House age",title="House age for different sizes of households")
```

The median house age of different sizes of households are less than 20 years, which is relatively stable as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Number.of.bedrooms))+geom_bar(aes(y=..prop..,fill=Number.of.bedrooms))+labs(x="Number of Family Members",y="Proportion",title="Number of bedrooms by different sizes of households")
```

As the number of family members increases, number of bedrooms increase, but for household with 5 family members, proportion of 7 bedrooms is incredibly high.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Electricity))+geom_bar(aes(y=..prop..,fill=Electricity),position="dodge")+labs(x="Number of Family Members",y="Proportion",title="Electricity by different sizes of households ")
```

For those small size households, the proportion wothout electricity is relatively high.

# format analysis

```{r}
# As the reponse variable is the number of people living in a household, which is counts data, we tend to use a poisson model to fit it.
data$Total.Number.of.Family.members=as.numeric(as.character(data$Total.Number.of.Family.members))
data$Number.of.bedrooms=as.numeric(as.character(data$Number.of.bedrooms))
model1=glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data,family = poisson)
model1%>%
  summary()
confint(model1)%>%
  kable()
```

```{r}
levels(data$Household.Head.Sex)
levels(data$Type.of.Household)
levels(data$Electricity)
```

The default baseline in R being taken as the one which comes first alphabetically. So these three categorical variables adopt female, Extended Family, 0 as baseline.

From the above summary we can observe that one continous explanaroty variable floor area is not significant and compared to extended family, Two or More Nonrelated Persons/Members is not significant while single family is significant.

So we can remove the house floor area variable firstly.

```{r}
model2=glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data,family = poisson)
model2%>%
  summary()
```

# Overdispersion

```{r}
ggplot(model2, aes(x=log(fitted(model2)), y=log((data$Total.Number.of.Family.members-fitted(model2))^2)))+
geom_point(col="#f46d43") +
geom_abline(slope=1, intercept=0, col="#a6d96a", linewidth=1) +
ylab(expression((y-hat(mu))^2)) + xlab(expression(hat(mu)))

```

From the above scatterplot of mean and variance, we can find most of the points lie above the line of equality for mean and variance. In this case, we are not to able to determine which explanatory variables are significant.

# Quasi-Poisson model

we can define a dispersion parameter $\phi$ such that $Var(Y_i)=\phi\mu_i$, we can estimate this parameter by $$\hat\phi=\frac{X^2}{n-p}$$

```{r}
X2=sum(resid(model2,type="pearson")^2)
dp=X2/model2$df.res
#With the use of the estimated dispersion parameter the Wald tests are not very reliable, so we turn to an F test to determine the significance of the regression coefficients:
drop1(model2,test="F")
```

After we try to fit a quasi-poisson model, the summary still shows all the remaining variables are significant.

# Negative binomial models

```{r}
model3=glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data)
summary(model3)
c(model2$deviance,model2$aic)
c(model3$deviance,model3$aic)
```

# final model

The final model is:$$Total.Number.of.Family.members=\beta_0+\beta_1\cdot Total.Household.Income+\beta_2\cdot Total.Food.Expenditure+\beta_3\cdot \mathbb{I}_{\mbox{Male}}(x)+\beta_4\cdot Household.Head.Age+\beta_5\cdot \mathbb{I}_{\mbox{Family}}(x)+\beta_6\cdot House.Age+\beta_7\cdot Number.of.bedrooms+\beta_8\cdot \mathbb{I}_{\mbox{Electricity}}(x)$$

$$\mathbb{I}_{\mbox{Male}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if the head of household is Male},\\
0 ~~~ \mbox{if the head of household is female}.\\
\end{array}
\right.$$


$$\mathbb{I}_{\mbox{Family}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{Single family},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.$$

$$\mathbb{I}_{\mbox{Electricity}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if the house has electricity},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.$$



For extended family and two or more nonrelated persons/members,
the final model is:
$$Total.Number.of.Family.members=1.596-2.532\times10^{-7}\cdot Total.Household.Income+2.953\times10^{-6}\cdot Total.Food.Expenditure+0.2634\cdot \mathbb{I}_{\mbox{Male}}(x)-3.852\times10^{-3}\cdot Household.Head.Age-3.760\times10^{-3}cdot House.Age+4.445\times10^{-2}\cdot Number.of.bedrooms-9.133\times10^{-2}\cdot \mathbb{I}_{\mbox{Electricity}}(x)$$

For single family, the final model is:
$$Total.Number.of.Family.members=1.596-2.532\times10^{-7}\cdot Total.Household.Income+2.953\times10^{-6}\cdot Total.Food.Expenditure+0.2634\cdot \mathbb{I}_{\mbox{Male}}(x)-3.852\times10^{-3}\cdot Household.Head.Age-3.760\times10^{-3}cdot House.Age+4.445\times10^{-2}\cdot Number.of.bedrooms-9.133\times10^{-2}\cdot \mathbb{I}_{\mbox{Electricity}}(x)-0.347$$