---
title: "Investigate which household related variables influence the number of people living in a household"
author: "Group 04"
number-sections: true
format: 
  html:
    embed-resources: true
    code-tools: true
  pdf: default
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  eval: true
  warning: false
  message: false
---

```{r}
#| label: libraries
library(ggplot2)
library(dplyr)
library(moderndive)
library(gapminder)
library(skimr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(knitr)
```

```{r}
#| label: data
data <- read_csv("dataset04.csv")
```

# Exploratory Data Analysis {#sec-EDA}

```{r}
summary <- data %>%
  skim()
summary_table <- skim_to_list(summary)
print(summary_table)
print(paste("Mean of the response variable:", mean(data$Total.Number.of.Family.members)))
print(paste("Variance of the response variable:", var(data$Total.Number.of.Family.members)))
```

We can see from the summary of the dataset that the mean of response variable (Total.Number.of.Family.members) is 4.53 and we calculate its variance is 4.91. This show that the difference between the mean and variance of response is not significantly large. Therefore, we may consider using Poisson Regression as our initial trial.

```{r}
#| label: fig-0
#| fig-cap: Distribution of Total Number of Family members 
ggplot(data = data, mapping = aes(x = Total.Number.of.Family.members)) +
  geom_histogram(bins = 60, color = "white", fill = "skyblue") +
  labs(x = "Total Number of Family members")
```

```{r}
#| label: fig-00
#| fig-cap: QQ-plot of Total Number of Family members 
qqnorm(data$Total.Number.of.Family.members)
qqline(data$Total.Number.of.Family.members)
```
From the @fig-0(Histogram) and the @fig-00(QQ-plot), the response variable seems not to fit a normal distribution, so we take the log transformation on the response variable.

```{r}
#| label: fig-log0
#| fig-cap: Distribution of Total Number of Family members after log transformation
ggplot(data = data, mapping = aes(x = log(Total.Number.of.Family.members))) +
  geom_histogram(bins = 60, color = "white", fill = "skyblue") +
  labs(x = "Total Number of Family members")
```

```{r}
#| label: fig-log00
#| fig-cap: QQ-plot of Total Number of Family members after log transformation
qqnorm(log(data$Total.Number.of.Family.members))
qqline(log(data$Total.Number.of.Family.members))
```
After using the log transformation the distribution is nearly normally distributed. (Is it good enough? Should we apply other methods to make some improvements?)

```{r}
#| label: fig-1
#| fig-cap: Total Number of Family members by Total Household Income
ggplot(data, aes(x = Total.Household.Income, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "Total Household Income", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-2
#| fig-cap: Total Number of Family members by Total Food Expenditure
ggplot(data, aes(x = Total.Food.Expenditure, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "Total Food Expenditure", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-3
#| fig-cap: Total Number of Family members by Household Head Sex
ggplot(data = data, mapping = aes(x = factor(Household.Head.Sex), y = Total.Number.of.Family.members)) +
  geom_boxplot(fill = "steelblue") +
  labs(x = "Total Head Sex", y = "Total Number of Family members")  
```

```{r}
#| label: fig-4
#| fig-cap: Total Number of Family members by Household Head Age
ggplot(data, aes(x = Household.Head.Age, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "Household Head Age", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-5
#| fig-cap: Total Number of Family members by Type of Household
ggplot(data = data, mapping = aes(x = factor(Type.of.Household), y = Total.Number.of.Family.members)) +
  geom_boxplot(fill = "steelblue") +
  labs(x = "Type of Household", y = "Total Number of Family members")  
```

```{r}
#| label: fig-6
#| fig-cap: Total Number of Family members by House Floor Area
ggplot(data, aes(x = House.Floor.Area, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "House Floor Area", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-7
#| fig-cap: Total Number of Family members by House Age
ggplot(data, aes(x = House.Age, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "House Age", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-8
#| fig-cap: Total Number of Family members by Number of bedrooms
ggplot(data, aes(x = Number.of.bedrooms, y = Total.Number.of.Family.members)) +
  geom_jitter() +
  labs(x = "Number of bedrooms", y = "Total Number of Family members") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
#| label: fig-9
#| fig-cap: Total Number of Family members by Electricity
ggplot(data = data, mapping = aes(x = factor(Electricity), y = Total.Number.of.Family.members)) +
  geom_boxplot(fill = "steelblue") +
  labs(x = "Electricity", y = "Total Number of Family members") +
  scale_x_discrete(labels = c("Do not have electricity", "Have electricity")) 
```

# Formal Data Analysis {#sec-FDA}

## Poisson Regression Model
```{r}
#| echo: true
model <- glm(Total.Number.of.Family.members ~ Total.Household.Income + Total.Food.Expenditure + Household.Head.Sex + Household.Head.Age + Type.of.Household + House.Floor.Area + House.Age + Number.of.bedrooms + Electricity, data = data, 
             family = poisson(link = "log"))
```

### Summary of the model
```{r}
summ(model)
```

```{r}
confint(model) %>%
  kable()
```
From the p-value and the 95% CI of estimates of coefficients above, we observed that
one class of the categorical variable Type.of.Household(Two or More Nonrelated Persons/Members) and continuous variable House.Floor.Area seem not to be statistically significant with the response variable.

### Remove House.Floor.Area
```{r}
#| echo: true
model_1 <- glm(Total.Number.of.Family.members ~ Total.Household.Income + Total.Food.Expenditure + Household.Head.Sex + Household.Head.Age + Type.of.Household + House.Age + Number.of.bedrooms + Electricity, data = data, 
             family = poisson(link = "log"))
```

```{r}
summ(model_1)
```
After removed the continuous variable House.Floor.Area, the AIC of the model almost remained the same, and the BIC of the model dropped a bit. So we can prove that House.Floor.Area does not influence response variable significantly.

### Remove Type.of.Household
```{r}
#| echo: true
model_2 <- glm(Total.Number.of.Family.members ~ Total.Household.Income + Total.Food.Expenditure + Household.Head.Sex + Household.Head.Age + House.Age + Number.of.bedrooms + Electricity, data = data, 
             family = poisson(link = "log"))
```

```{r}
summ(model_2)
```
However, if we removed the categorical variable Type.of.Household from the model, the AIC and BIC both increased. Therefore, we cannot conclude that Type.of.Household will not influence the response variable.
