---
title: "DAS-Project2"
author: "Yiheng Yang, Yuanqing Zhang"
number-sections: true
format: 
  html:
    embed-resources: true
    code-tools: true
  pdf: default
editor_options: 
  chunk_output_type: console
execute:
  echo: true
  eval: true
  warning: false
  message: false
---

# Introduction

The Family Income and Expenditure Survey is conducted in Philippines every three years, which provides data about income and expenditure of family. The dataset contains information about the household income, food expenditure, floor area of house and so on. This analysis aims to find which household variables that influence the number of people living in a household.

# Load the data

```{r}
#| label: data
data=read.csv("dataset04.csv")
```

# Get packages

```{r}
#| label: libraries
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(tidyverse)
library(ggplot2)
library(MASS)
library(knitr)
library(tidyr)
library(gt)
library(janitor)
library(skimr)
library(kableExtra)
library(gridExtra)
```

# Exploratory Data Analysis {#sec-EDA}

## Summary of response variable

```{r}
data%>%summarize('Mean' = mean(Total.Number.of.Family.members),
'Median' = median(Total.Number.of.Family.members),
'St.Dev' = sd(Total.Number.of.Family.members),
'Variance'=var(Total.Number.of.Family.members),
'Min' = min(Total.Number.of.Family.members),
'Max' = max(Total.Number.of.Family.members),
'IQR' = quantile(Total.Number.of.Family.members,0.75)
-quantile(Total.Number.of.Family.members,0.25),
'Sample_size' = n())%>% 
  gt()%>%
  fmt_number(decimals=2)%>%
  cols_label(
Mean = html("Mean"),
Median = html("Median"),
St.Dev = html("Std. Dev"),
Variance=html("Variance"),
Min = html("Minimum"),
Max = html("Maximum"),
IQR = html("Interquartile Range"),
Sample_size = html("Sample Size"))
```

We can see from this numerical summary, the mean of number of family members is 4.53 and the variance is 4.91. If variance is bigger than mean, we can determine that we have overdispersion. We will investigate this phenomenon later.

## Convert some categorical variables to factors

```{r}
data$Household.Head.Sex=as.factor(data$Household.Head.Sex)
data$Type.of.Household=as.factor(data$Type.of.Household)
data$Electricity=as.factor(data$Electricity)
levels(data$Electricity)=c("No","Yes")
data$Number.of.bedrooms=as.factor(data$Number.of.bedrooms)
levels(data$Number.of.bedrooms)=c("0","1","2","3","4","5","6","7")
```

## Summary of categorical explanatory variables

```{r}
data_categorical=data%>%
  dplyr::select("Household.Head.Sex","Type.of.Household","Electricity")
summary(data_categorical)
```

The numerical summary shows that male owners, single families and households with electricity account for a major proportion.

## Summary of numerical explanatory variables

```{r}
data_numerical=data[,c(1,3,5,7,8,9,10)]
data_numerical$Number.of.bedrooms=as.numeric(as.character(data_numerical$Number.of.bedrooms))
my_skim <- skim_with(numeric = sfl(hist = NULL), 
                  base = sfl(n = length))
my_skim(data_numerical) %>%
  transmute(Variable=skim_variable, Sample_size = n, Mean=numeric.mean, St.Dev=numeric.sd,
            Min=numeric.p0, Median=numeric.p50,  Max=numeric.p100,
            IQR = numeric.p75-numeric.p50) %>%
  kable(format.args = list(big.mark = ","), digits=2) %>%
  kable_styling(font_size = 10, latex_options = "hold_position")
```

## Graphical summaries

As we want to plot a boxplot with x axis to be number of family members, so we need to change this variable to be a factor.

```{r}
data$Total.Number.of.Family.members=as.factor(data$Total.Number.of.Family.members)
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members))+geom_bar()
```

The boxplot shows that household with four family members accounts for the largest proportion. Most of the data is consisted of families with three to five family members.

```{r}
p1=ggplot(data=data,aes(y=Total.Household.Income))+geom_boxplot()+labs(y="Total household income",title="Boxplot of total household income")
p2=ggplot(data=data,(aes(y=Total.Food.Expenditure)))+geom_boxplot()+labs(y="Total food expenditure",title="Boxplot of total food expenditure")
p3=ggplot(data=data,aes(x="",fill=Household.Head.Sex))+geom_bar(width=1)+coord_polar(theta="y")+labs(y="count",title="Pie chart of sex distribution")
p4=ggplot(data=data,aes(y=Household.Head.Age))+geom_boxplot()+labs(y="Household head age",title="Boxplot of household head age")
p5=ggplot(data=data,aes(x=Type.of.Household))+geom_bar(aes(fill=Type.of.Household))+scale_x_discrete(labels=c("Entended","Single","Two or More"))+labs(x="Type of household",y="Count",title="Barplot of type of household")
p6=ggplot(data=data,aes(y=House.Floor.Area))+geom_boxplot()+labs(y="House floor area",title="Boxplot of house floor area")
p7=ggplot(data=data,aes(y=House.Age))+geom_boxplot()+labs(y="House age",title="Boxplot of house age")
p8=ggplot(data=data,aes(x=Number.of.bedrooms))+geom_bar(aes(fill=Number.of.bedrooms))+labs(x="Number of bedrooms",y="Count",title="Barplot of number of bedrooms")+theme(legend.position = "none")
p9=ggplot(data=data,aes(x=Electricity))+geom_bar(aes(fill=Electricity))+labs(y="Count",title="Barplot of electricity")
```

```{r}
grid.arrange(p1,p2)
grid.arrange(p3,p5,p8,p9)
grid.arrange(p4,p6,p7)
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Total.Household.Income,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Total Household Income",title="Income of families with different number of family members ")
```

We can see from the above boxplot that the median of household income increase as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Total.Food.Expenditure,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Total food expenditure",title="Food expenditure of families with different number of family members")
```

The boxplot indicates that median increase significantly as the number of family members increase. Household with 19 members have the largest variance in food expenditure.

```{r}
data%>%
  tabyl(Household.Head.Sex,Total.Number.of.Family.members)%>%
  adorn_percentages()%>%
  adorn_pct_formatting()%>%
  adorn_ns()
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Household.Head.Sex))+geom_bar(aes(y=..prop..,fill=Household.Head.Sex),position="dodge")+labs(x="Number of Family Members",y="Proportion",title="Head sex proportion for different size of households")
```

We can see from the barplot, for those small sized households, the proportion is much higher for females than for males. However, this situation does not exist for those household with four or more family members.

```{r}
ggplot(data=data,aes(x=Household.Head.Sex,y=as.numeric(as.character(Total.Number.of.Family.members))))+geom_boxplot(aes(fill=Household.Head.Sex))+labs(x="Household head sex",y="Number of family members",title="Number of family members by sex")
```

We can conclude from the boxplot that households tend to have more family members if their owner is male.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=Household.Head.Age,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="Household head age",title="Head age for different size households")
```

For different size of households, the median of household head age remain at a constant level around 50.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Type.of.Household))+geom_bar(aes(y=..prop..,fill=Type.of.Household))+labs(x="Number of Family Members",y="Proportion",title="Type of household in different size of households")
```

These families with two or more nonrelated members only exist in medium size household. As total family members increase more than 8, single family account for a very small proportion.

```{r}
ggplot(data=data,aes(x=Type.of.Household,y=as.numeric(as.character(Total.Number.of.Family.members))))+geom_boxplot(aes(fill=Type.of.Household))+scale_x_discrete(labels=c("Extended","Single","Two or more"))+labs(x="Type of household",y="Number of family members",title="Number of family members by type of household")+theme(legend.position = "bottom")
```

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=House.Floor.Area,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="House floor area",title="House floor area for different size of households")
```

For different sizes of households, there are a few outliers. And the median of house floor area seems to be stable as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,y=House.Age,fill=Total.Number.of.Family.members))+geom_boxplot()+theme(legend.position = "none")+labs(x="Number of Family Members",y="House age",title="House age for different sizes of households")
```

The median house age of different sizes of households are less than 20 years, which is relatively stable as number of family members increase.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Number.of.bedrooms))+geom_bar(aes(y=..prop..,fill=Number.of.bedrooms))+labs(x="Number of Family Members",y="Proportion",title="Number of bedrooms by different sizes of households")
```

As the number of family members increases, number of bedrooms increase, but for household with 5 family members, proportion of 7 bedrooms is incredibly high.

```{r}
ggplot(data=data,aes(x=Total.Number.of.Family.members,group=Electricity))+geom_bar(aes(y=..prop..,fill=Electricity),position="dodge")+labs(x="Number of Family Members",y="Proportion",title="Electricity by different sizes of households ")
```

For those small size households, the proportion wothout electricity is relatively high.

```{r}
ggplot(data=data,aes(x=Electricity,y=as.numeric(as.character(Total.Number.of.Family.members))))+geom_boxplot(aes(fill=Electricity))+labs(x="Electricity",y="Number of family members",title="Number of family members by electricity")
```

From the above boxplot, households with electricity and without electricity have the same distribution of family members.

# Formal analysis {#sec-FDA}

## Poisson Regression Model

```{r}
# As the response variable is the number of people living in a household, which is counts data, we tend to use a poisson model to fit it.
data$Total.Number.of.Family.members=as.numeric(as.character(data$Total.Number.of.Family.members))
data$Number.of.bedrooms=as.numeric(as.character(data$Number.of.bedrooms))
model1=glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data,family = poisson)
model1%>%
  summary()
confint(model1)%>%
  kable()
```

```{r}
levels(data$Household.Head.Sex)
levels(data$Type.of.Household)
levels(data$Electricity)
```

The default baseline in R being taken as the one which comes first alphabetically. So these three categorical variables adopt female, Extended Family, No as baseline.

From the above summary we can observe that one continuous explanatory variable floor area is not significant and compared to extended family, Two or More Nonrelated Persons/Members is not significant while single family is significant according to the p-value and the 95% CI of estimates of coefficients.

### Rate Ratio

```{r}
model_summary <- summary(model1)
coef <- model_summary$coefficients[,1]
std_err <- model_summary$coefficients[,2]
rate_ratio <- exp(model_summary$coef)
conf_interval <- exp(cbind(coef - 1.96 * std_err, coef + 1.96 * std_err))
result <- data.frame(coef = coef, std_err = std_err, rate_ratio = rate_ratio, conf_interval)
print(result)
```

The result from the rate ratio agree with that from p-values and confidence intervals. We can observe that the type "Two or More Nonrelated Persons/Members" is not significantly different compared to the baseline "Extended family". So we can firstly merge these two kinds of types of household to "Not Single", while another is "Single Family".

```{r}
data1=read.csv("dataset04.csv") # for conviniency, introduce a new dataset, which we can merge these two kinds of type of households in it without changing the original dataset.
data1[data1$Type.of.Household!="Single Family",]$Type.of.Household="Not Single"
```

### Fit model on the merged dataset

```{r}
model2=glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)
model2%>%
  summary()
```

we can find the variable floor area is still not significant, so we remove it then.

### Remove floor area

```{r}
model3=glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)
```

```{r}
model3%>%
  summary()
```

The final model's vairables are all significant now, with an aic value of 8510.4

## Overdispersion

```{r}
ggplot(model2, aes(x=log(fitted(model2)), y=log((data$Total.Number.of.Family.members-fitted(model2))^2)))+
geom_point(col="#f46d43") +
geom_abline(slope=1, intercept=0, col="#a6d96a", linewidth=1) +
ylab(expression((y-hat(mu))^2)) + xlab(expression(hat(mu)))

```

From the above scatterplot of mean and variance, we can find most of the points lie above the line of equality for mean and variance. In this case, we are not to able to determine which explanatory variables are significant.

### Examine existence of dispersion

```{r}
library(qcc)
qcc.overdispersion.test(data$Total.Number.of.Family.members)
```

From the dispersion test we know that the p-value\<0.05,indicating that the dispersion does exist in number of family members. So we should consider to fit a Quasi-Poisson model or a negative binomial model to the data.

### Quasi-Poisson model

we can define a dispersion parameter $\phi$ such that $Var(Y_i)=\phi\mu_i$, we can estimate this parameter by $$\hat\phi=\frac{X^2}{n-p}$$

```{r}
X2=sum(resid(model1,type="pearson")^2)
dp=X2/model1$df.res
#With the use of the estimated dispersion parameter the Wald tests are not very reliable, so we turn to an F test to determine the significance of the regression coefficients:
drop1(model1,test="F")
```

From the model summary above, we are supposed to delete the variable House.Floor.Area.

```{r}
model_quasi <- glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data,family = quasipoisson(link = "log"))
summary(model_quasi)
```

In a Quasi-Poisson model, Two or More Nonrelated Persons/Members is still not significantly different compared to Extended Family. So we need to fit this model again using merged dataset.

```{r}
model_quasi_1 <- glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data1,family = quasipoisson(link = "log"))
summary(model_quasi_1)
```

Then we need to remove the floor area variable.

```{r}
model_quasi_2 <- glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = quasipoisson(link = "log"))
summary(model_quasi_2)
```

Using the Quasi-Poisson model, we reach the same conclusion as what we get in the ordinary glm model, which removes only floor area variable.

### Negative binomial models

Considering the Overdispersion, another choice is the Negative-binomial model.

```{r}
model_nb=glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data)
summary(model_nb)
```

Similarly, we can see that the categorical variable Type.of.Household(Two or More Nonrelated Persons/Members) and continuous variable House.Floor.Area seem not to be statistically significant with the response variable.

```{r}
model_nb1 <- glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Floor.Area+House.Age+Number.of.bedrooms+Electricity,data=data1)
summary(model_nb1)
model_nb1$aic
```

We firstly fit a negative model using the merged dataset and find the floor area is still not significant. So we need to remove it in our next model.

```{r}
model_nb2 <- glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)
summary(model_nb2)
model_nb2$aic
```

Using the negative binomial model, all the variables except floor area are significant.

### Using AIC to choose best model

#### GLM model

```{r}
c(glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+House.Age+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+Number.of.bedrooms+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Electricity,data=data1,family = poisson)$aic,
glm(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms,data=data1,family = poisson)$aic)
```

| Removed variable       | AIC value |
|------------------------|-----------|
| None                   | 8510.362  |
| Total.Household.Income | 8530.664  |
| Total.Food.Expenditure | 8694.374  |
| Household.Head.Sex     | 8587.067  |
| Household.Head.Age     | 8530.923  |
| Type.of.Household      | 8731.536  |
| House.Age              | 8521.788  |
| Number.of.bedrooms     | 8522.761  |
| Electricity            | 8518.495  |

In ordinary GLM model, the full model with all explanatory variables has the lowest AIC value.

#### Negative binomial model

```{r}
c(glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Type.of.Household+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+House.Age+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+Number.of.bedrooms+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Electricity,data=data1)$aic,
glm.nb(Total.Number.of.Family.members~Total.Household.Income+Total.Food.Expenditure+Household.Head.Sex+Household.Head.Age+Type.of.Household+House.Age+Number.of.bedrooms,data=data1)$aic)
```

| Removed variable       | AIC value |
|------------------------|-----------|
| None                   | 8512.384  |
| Total.Household.Income | 8532.686  |
| Total.Food.Expenditure | 8696.396  |
| Household.Head.Sex     | 8589.086  |
| Household.Head.Age     | 8532.944  |
| Type.of.Household      | 8733.542  |
| House.Age              | 8523.809  |
| Number.of.bedrooms     | 8524.781  |
| Electricity            | 8520.517  |

# Final model
We find that GLM model with only floor area variable removed has the lowest AIC value.

The final model is:$$log(Total.Number.of.Family.members)=\beta_0+\beta_1\cdot Total.Household.Income+\beta_2\cdot Total.Food.Expenditure+\beta_3\cdot \mathbb{I}_{\mbox{Male}}(x)+\beta_4\cdot Household.Head.Age+\beta_5\cdot \mathbb{I}_{\mbox{Family}}(x)+\beta_6\cdot House.Age+\beta_7\cdot Number.of.bedrooms+\beta_8\cdot \mathbb{I}_{\mbox{Electricity}}(x)$$

$$\mathbb{I}_{\mbox{Male}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if the head of household is Male},\\
0 ~~~ \mbox{if the head of household is female}.\\
\end{array}
\right.$$

$$\mathbb{I}_{\mbox{Family}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{Single family},\\
0 ~~~ \mbox{Not Single Family}.\\
\end{array}
\right.$$

$$\mathbb{I}_{\mbox{Electricity}}(x)=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if the house has electricity},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.$$

For extended family and two or more nonrelated persons/members, the final model is: $$log(Total.Number.of.Family.members)=1.594-2.531\times10^{-7}\cdot Total.Household.Income+2.937\times10^{-6}\cdot Total.Food.Expenditure+0.2633\cdot \mathbb{I}_{\mbox{Male}}(x)-3.837\times10^{-3}\cdot Household.Head.Age-3.742\times10^{-3}cdot House.Age+4.454\times10^{-2}\cdot Number.of.bedrooms-9.140\times10^{-2}\cdot \mathbb{I}_{\mbox{Electricity}}(x)$$

For single family, the final model is: $$log(Total.Number.of.Family.members)=1.25-2.531\times10^{-7}\cdot Total.Household.Income+2.937\times10^{-6}\cdot Total.Food.Expenditure+0.2633\cdot \mathbb{I}_{\mbox{Male}}(x)-3.837\times10^{-3}\cdot Household.Head.Age-3.742\times10^{-3}cdot House.Age+4.454\times10^{-2}\cdot Number.of.bedrooms-9.140\times10^{-2}\cdot \mathbb{I}_{\mbox{Electricity}}(x)$$

# Conclusion

Variables Total.Household.Income, Total.Food.Expenditure, Household.Head.Sex, Household.Head.Age, Type.of.Household, House.Age, Number.of.bedrooms and Electricity could influence response variable Total.Number.of.Family.members.
